|

### 2025-01-10 output/seminar-slideshow.qmd
Tweak style in direction cosine properties slide

ITEMS_PALETTE <- c(
  PALETTE_BLUE["normal"],
  PALETTE_RASPBERRY["normal"],
  PALETTE_APPLE["normal"],
  PALETTE_TANGERINE["normal"],
  PALETTE_UNED["normal"]
) |>
  unname() |>
  setNames(1:5)

@@

::: {.r-stack style="color:#00533e;"}
$$
  \begin{matrix}
    \mathbf{a}_5 \approx \begin{bmatrix}
        2 \\
        0
      \end{bmatrix} &
      \mathbf{\alpha}_5 =  \begin{bmatrix}
         0º \\
        90º
      \end{bmatrix}
  \end{matrix}
$$
:::
:::::

>>>>

ITEMS_PALETTE <- c(
  PALETTE_BLUE["normal"],
  PALETTE_RASPBERRY["normal"],
  PALETTE_APPLE["normal"],
  PALETTE_TANGERINE["normal"],
  PALETTE_UNED["medium"]
) |>
  unname() |>
  setNames(1:5)

@@

::: {.r-stack style="color:#427562;"}
$$
  \begin{matrix}
    \mathbf{a}_5 \approx \begin{bmatrix}
        2 \\
        0
      \end{bmatrix} &
      \mathbf{\alpha}_5 =  \begin{bmatrix}
         0º \\
        90º
      \end{bmatrix}
  \end{matrix}
$$
:::
:::::
